Changelog

### 2021-05-23 changelog.tex
Updates from Overleaf

\section{Requested Changes}

\begin{enumerate}
\item Fuzzing – need stronger motivation.
\item Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.
\item Can you extend your research (especially the quantification part) to include other side channel signals?
\item A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.
\item iid assumption – does it fit your research on side-channel?
\item Some feedback I gave before your defense.

Before the defense, Dr. Wu gave me the following feedback.
\end{enumerate}
\section{Other Changes}

>>>>

\begin{enumerate}
\item \textbf{Fuzzing – need stronger motivation.}
\item \textbf{Discuss the limitations of your research
e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.}
\item \textbf{Can you extend your research (especially the quantification part) to include other side channel signals?}

It is possible to extend the quantification part to include other side channel signals. The key here is to model the noise in reality. In my dissertation, I assume an attacker can have a noise-free observation. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}
\item \textbf{iid assumption – does it fit your research on side-channel?}

\item \textbf{Some feedback I gave before your defense.}

As suggested by Dr. Wu, I added a new chapter on Discussion and Limitations, and discussed potential ways and related work to the mitigated reported side.

\item \textbf{Improve Grammar.}

Dr. Larus helped me fix many grammar issues. I have revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
\end{enumerate}

I have Incorporated some discussions into my dissertation. Please let me know if you have any feedback.
